How to compute the fusion product of MV cycles in type A

### 2021-03-10 draft.tex
goodbye original falling action
some explanation of how to apply ES

    \item The locus $\cW_\mu = G_1\xt[t^{-1}] t^\mu \subset \Grth $.  
    \acom{What goes wrong if we take $G_1[t^{-1}]t^\mu$ instead?} \jcom{Then it lives in the thin Grassmannian.  And unless $ A $ is nilpotent, then $g(A)$ won't live there.}
    In modular terms, this corresponds to the locus of those $ (V, \varphi)$ such that $ V $ is isomorphic to the trivial vector bundle on $ \PP$ and such that $ \varphi$ preserves the {Harder--Narasimhan filtration of $V$ at $ \infty$}.  The lattice description of $ \cW_\mu \cap \Grth^+$ is given in Lemma \ref{le:Wmu} below. 
    % \acom{que est-ce?} \jcom{It's not very relevant for this paper.  Here is an explanation: every vector bundle on $\PP$ (or maybe any curve) has a special filtration called the HN--filtration; it is a partial flag of subbundles of type determined by $ \mu$.  We require that $ \varphi$ takes this filtration to the standard partial flag at the fibre over $ \infty$.  Maybe ``preserves'' is not the best word above.}
    % A: Ok thanks!
    % 
    \item The semi-infinite orbit $ S^\mu = N(\cK)t^\mu \subset \Gr $.  
    \item The family of semi-infinite orbits $ S^{\mu_1, \mu_2}_{0,\AA} := S^{\mu_1} \ast_\AA S^{\mu_2}$.  If $ s \ne 0 $, then the fibre $S^{\mu_1, \mu_2}_{0,s} $ is given by
    $$
    S^{\mu_1, \mu_2}_{0,s} = N(\CC[t, t^{-1}, (t-s)^{-1}])t^{\mu_1} (t-s)^{\mu_2} G(\CC[t])\subset G(\CC[t,t^{-1}, (t-s)^{-1}]) / G(\CC[t]) \,. % \G(\CC[t])
    $$
    % TODO: resolve
    % \jcom{Maybe we should introduce the $ L_{\mu_1, \mu_2} $ notation, but I'm not sure it is necessary.}
    On the other hand, if $ s = 0$, then the fibre $S^{\mu_1, \mu_2}_{0,0} $ equals $ S^{\mu_1 + \mu_2}$. 
    % TODO: resolve
    % \acom{changed $\mu$ to $\mu_1 + \mu_2$ since we wrote it out for $\overline{\Gr}_{0,\AA}^{\lambda_1, \lambda_2} $}

@@

@@

\begin{lemma} \label{le:Wmu}
    Let $ L \in \Grth^+$.  The following are equivalent:
    \begin{enumerate}
        \item $ L \in \cW_\mu$.
                \item $ L = \Sp_\cO(v_1, \dots, v_m)$ for some $ v_i $ of the form $ v_i = t^{\mu_i} e_i + \sum_{j=1}^m p_{ij} e_j $ where $ p_{ij} \in \CC[t] $ has degree less than $ \min(\mu_i, \mu_j)$. \acom{Do we want to sum over $j \ne i$ here? Maybe nvm because in $\TT_\mu$ the diagonal blocks can have $*$'s in the last row. Also $\cO$ sb $\CC[t]$.}
        \item  For all $ i $, 
        $$ t^{\mu_i} e_i \in \Sp_\CC(\{t^k e_j : 0 \le k < \min(\mu_i, \mu_j), 1 \le j \le m \}) + L. $$
    \end{enumerate}
    Moreover, for such $L $, $ \beta_\mu := \{ [t^k e_i] : 0 \le k < \mu_i, 1 \le i \le m\}$ forms a basis for $ L_0/L$.
\end{lemma}

@@

\begin{proof}
    Let $ L \in \cW_\mu$.  Then $ L = \Sp_\cO(v_1, \dots, v_m) $ for some $ v_i $ with $ v_i = t^{\mu_i} e_i + \sum_{j=1} q_{ij}t^{\mu_i} e_j $ and $ q_{ij} \in t^{-1} \CC\xt[t^{-1}]$.  Since $ L \in \Grth^+ $, we see that $ v_i \in L_0$ which means that $ p_{ij} := q_{ij}t^{\mu_i} $ lies in $ \CC[t]$.  By construction, the polynomial $ p_{ij}$ has degree less than $ \mu_i$.

@@

\begin{proof}
    Let $ L $ lie in this image.  Then $ L = g t^{\mu_1} (t-s)^{\mu_2}$ fom some $ g \in N(\CC[t, t^{-1}, (t-s)^{-1}]) $.  Let $ h =(t-s)^{\mu_2} t^{-\mu_2}  $.  Note that $ h \in T_1(\CC\xt[t^{-1}])$. 
    Moreover,
    $$ L = h (h^{-1} g h) t^{\mu}\,. $$
    Note that 
    % $ h^{-1} g h \in N(\CC\xT[t^{-1}])$ 
    $h^{-1} g h \in N(\cK_\infty)$ and from \cite{kamnitzer2014yangians} 
    \jcom{Check this}, we know that $ (h^{-1} g h) t^{\mu} \in \cW_\mu$ and so the result follows.

    \acom{
        % The argument from my thesis does not go through since $\cW_\mu$ is defined mod $\CC[t]$. More precisely, we still have $N(\Kinf) = N_1(\CC[t]) N(\CC\xt[t^{-1}])$ and so $h^{-1}g h=g_1g_2$ for some $g_1 \in N_1(\CC[t])$ for some $g_2\in N\xt[t^{-1}]$. But now we would like to write $g_2 t^\mu = t^\mu g_3$ for some $g_3\in\CC[t]$. Oh, but I guess we can also 
        To check this write $N(\Kinf) = N_1(\CC\xt[t^{-1}])N(\CC[t])$. Does it hold? If $\mu$ is dominant and $g\in N(\CC[t])$ then $gt^\mu = t^\mu g'$ for some $g'\in N(\CC[t])$.} % What is a textbook reference for these factorization claims? are they obvious; they seem obvi
        \jcom{Yes, that is correct.  I think that I once had Alex write out a careful proof of this fact.  It holds for any unipotent group.  The proof is by induction.}
    \end{proof}

\section{Climax}
Given $ A \in \TT_\mu$, recall the definition of $ g(A)$ given in \Cref{eq:mvyofa}.
% section ??.  
As $ g(A) \in M_n(\CC[t]) \cap G_1(\CC\xt[t^{-1}])$, we will regard $ g(A)$ as giving an element of $ \Grth^+ \cap \cW_\mu$.

@@

 On the other hand, if $ (g(A), s) \in S^{\mu_1, \mu_2}_\AA$, then we can write 
 $$
 g t^\mu r= n t^{\mu_1} (t-s)^{\mu_2}
$$
for some $ r \in G(\CC[t]), n \in N[t, t^{-1}, (t-s)^{-1}] $ and $ g = g(A)t^{-\mu}$.  Let $ h = (t-s)^{\mu_2} t^{-\mu_2}$ which lies in $ T_1\xt[t^{-1}] $.
Note that $ h^{-1}n h \in N(\Kinf)$, 
% ((t^{-1}))
so we can factor it as $ n = n_1 n_2 $, where $ n_1 \in N_1(\CC\xt[t^{-1}]), n_2 \in N(\CC[t])$.  So then after doing a bit of algebra, we reach
$$
t^\mu r (t^{-\mu} n_2 t^\mu) t^{-\mu} = g^{-1} h n_1.
$$
The right hand side $ g^{-1} h n_1 $ lies in $ G_1(\CC\xt[t^{-1}]) $.  Now on the left hand side, we know that since $ \mu $ is dominant $ t^{-\mu} n_2 t^\mu \in N(\CC[t])$.  
Moreover since $ \mu $ is dominant, we know that 
$$t^\mu G(\cO) t^{-\mu} \cap G_1(\CC\xt[t^{-1}]) = N_1(\CC\xt[t^{-1}]\,.$$
Thus, we deduce that $ g^{-1} h n_1 \in N_1(\CC\xt[t^{-1}])$ and hence $ g(A) \in N_1(\CC\xt[t^{-1}]) t^{\mu_1} (t-s)^{\mu_2} $.  Given that we know that $ A \in \TT_\mu $, this implies that $ (A,s) \in \UU^{\mu_1, \mu_2}_\AA$ as desired.
\end{proof}

@@

\section{Falling Action} % Resolution

\begin{theorem}
    Let $\lambda_i\ge\mu_i$ be dominant ($i=1,2$), $\mu = \mu_1 +\mu_2$, and $\lambda =\lambda_1+\lambda_2$. 
    % I have an irrational dislike of ending sentences with subscripts --- can we fix this?
    There is an isomorphism 
    \begin{equation}
        \overline{\OO}_{\lambda_1,\lambda_2}\cap\TT_{\mu_1,\mu_2} \to \overline\Gr_\AA^{\lambda_1,\lambda_2}\cap \cW_{\mu_1,\mu_2}
    \end{equation}
    got by taking a $\mu\times\mu$ block matrix $A$ in the $s$-fibre $\overline{\OO_{\lambda_1,\lambda_2}^s}\cap\TT_{\mu_1,\mu_2}^s$ on the left to the representative of the $s$-fibre on the right defined by  
    \begin{equation}
        \begin{split}
            g &= t^{\mu_1} (t-s)^{\mu_2} + a(t) \\
            a_{ij}(t) &= - \sum_{k=1}^{\mu_i} A^k_{ji} t^{k-1}
        \end{split}
    \end{equation}
    where $A^k_{ji}$ is the $k$th entry from the left of the last row of the $\mu_j\times\mu_i$ block of $A$. 
\end{theorem}

@@

\begin{proof}
    % Copy Roger's proof.
    We have
\[
\begin{split}
    S_{\mu_1, \mu_2} & = N\xT[t^{-1}]t^{\mu_1}(t-s)^{\mu_2} \\
     & \subset T_1\xt[t^{-1}] N\xT[t^{-1}] t^{\mu_1} (t-s)^{\mu_2} \\
     & = T_1\xt[t^{-1}] N_1\xt[t^{-1}] t^{\mu_1} (t-s)^{\mu_2} \qquad \text{\cite[Lemma 2.3]{kamnitzer2014yangians}}\\
     & = B_1\xt[t^{-1}] t^{\mu_1} (t-s)^{\mu_2} \\
     & = B_1\xt[t^{-1}] t^{\mu_1 + \mu_2} \\
     & \subset G_1\xt[t^{-1}] t^{\mu_1 + \mu_2} \\
     & = W_{\mu_1 + \mu_2}
\end{split}
\]
where $B_1\xt[t^{-1}] t^{\mu_1} (t-s)^{\mu_2} = B_1\xt[t^{-1}] t^{\mu_1 + \mu_2}$ since 
\[
\frac{t}{t-s} = 
1 + \frac{s}{t} + \frac{s^2}{t^2} + \cdots 
\in B_1\xt[t^{-1}].
\]
\end{proof}

@@

>>>>

    \item The locus $\cW_\mu = G_1\xt[t^{-1}] t^\mu \subset \Grth $.  
    \acom{What goes wrong if we take $G_1[t^{-1}]t^\mu$ instead?} \jcom{Then it lives in the thin Grassmannian.  And unless $ A $ is nilpotent, then $g(A)$ won't live there.} \acom{Another notational thing is $G_1\xt[t^{-1}] = G_1(\CC\xt[t^{-1}])$ and in our paper this short hand is only used for these kernel subgroups.}
    In modular terms, this corresponds to the locus of those $ (V, \varphi)$ such that $ V $ is isomorphic to the trivial vector bundle on $ \PP$ and such that $ \varphi$ preserves the {Harder--Narasimhan filtration of $V$ at $ \infty$}.  The lattice description of $ \cW_\mu \cap \Grth^+$ is given in Lemma \ref{le:Wmu} below. 
    % \acom{que est-ce?} \jcom{It's not very relevant for this paper.  Here is an explanation: every vector bundle on $\PP$ (or maybe any curve) has a special filtration called the HN--filtration; it is a partial flag of subbundles of type determined by $ \mu$.  We require that $ \varphi$ takes this filtration to the standard partial flag at the fibre over $ \infty$.  Maybe ``preserves'' is not the best word above.}
    % A: Ok thanks!
    % 
    \item The semi-infinite orbit $ S^\mu = N(\cK)t^\mu \subset \Gr $.  
    \item The family of semi-infinite orbits $ S^{\mu_1, \mu_2}_{0,\AA} := S^{\mu_1} \ast_\AA S^{\mu_2}$.  If $ s \ne 0 $, then the fibre $S^{\mu_1, \mu_2}_{0,s} $ is given by
    $$
    S^{\mu_1, \mu_2}_{0,s} = N(\CC[t, t^{-1}, (t-s)^{-1}])t^{\mu_1} (t-s)^{\mu_2} G(\CC[t])\subset G(\CC[t,t^{-1}, (t-s)^{-1}]) / G(\CC[t]) \,. % \G(\CC[t])
    $$
    % TODO: resolve
    % \jcom{Maybe we should introduce the $ L_{\mu_1, \mu_2} $ notation, but I'm not sure it is necessary.}
    On the other hand, if $ s = 0$, then the fibre $S^{\mu_1, \mu_2}_{0,0} $ equals $ S^{\mu_1 + \mu_2}$. 
    % TODO: resolve
    % \acom{changed $\mu$ to $\mu_1 + \mu_2$ since we wrote it out for $\overline{\Gr}_{0,\AA}^{\lambda_1, \lambda_2} $}

@@

\acom{The following is a rough note.}

The relevant result from Eisenbud--Saltman seems to be that 
$$X_r = X_{r,0} = \{A:\rk A^i \le r(i) \}$$ 
is the flat limit of 
$$X_{r,\lambda} = \{A : \rk (A-\lambda_i)^j\le r(i,j)\}$$
with $r(i,j)$ determined by $r(i)$.

The case that we are interested in is the case of two eigenvalues. Let me change notation so that $\lambda_i$ are shapes and let me only look at the open loci where the rank conditions are strict.

Let $m_i = \lambda_{i,1}$ ($i = 1,2$), $m = m_1 + m_2$, and define
$$r(j) = N - \#\text{~boxes in first $j$ columns of }\lambda_1 + \lambda_2 = \lambda\vdash N$$
on $j = 1,\dots,m$. Note that $r(j-1) - r(j)$ is the length of the $j$th column of $\lambda$. As in \cite{eisenbud1989rank} we will denote this quantity $a_j$. 
%

Next, take $p$ to be a permutation of the (lengths of) columns $a_j$ of $\lambda$ such that $a_{p(1)},\dots,a_{p(m_1)}$ are the (lengths of) columns of $\lambda_1$ and $a_{p(m_1 + 1)},\dots, a_{p(m_1 + m_2)}$ are the (lengths of) columns of $\lambda_2$. 
Then the functions 
$$
r(1,j) = N - a_{p(1)} - \cdots - a_{p(j)} \text{ and } r(2,j) = N - a_{p(m_1 + 1)} - \cdots - a_{p(m_1 + j)}
$$
are such that 
\begin{align*}
    \OO^{\lambda_1,\lambda_2} = X_{r,(0,s)} = \{A:\rk A^j &= r(1,j) \text{ for } i = 1,\dots,\lambda_{1,1} \\ \text{ and } \rk (A-s)^j &= r(2,j) \text{ for } i = \lambda_{1,1} + 1 ,\dots, \lambda_{2,1} \}
\end{align*}
and according to \cite[Theorem 2.1(iii)]{eisenbud1989rank} the family $X_{r,\AA^m}$ is flat over $\AA^m$ with zero fibre $X_{r,0} = \OO^\lambda$ as desired.

% On the one hand, we know that $r(i,j)$ should be equal to $N$ minus the number of boxes in the first $j$ columns of $\lambda_i$. On the other hand, ES define $r(i,j)$ to be $N$ minus the $i$th chunk of $j$ columns determined by the rank function $r(i)$. Also, we would like for $r(i)$ to determine the shape $\lambda = \lambda_1 + \lambda_2$. Take for example $\lambda_1 = \lambda_2 = (2,1)$. Then $\lambda = (4,2)$ and so $r\{0,1,2,3,4\}=\{6,4,2,1,0\}$ and 
% $$\{a_1,a_2,a_3,a_4\} = \{6-4,4-2,2-1,1-0\}=\{2,2,1,1\}\,.$$

% For another example take $\lambda_1 = (1)$ and $\lambda_2 = (1,1)$. Then $\lambda = (2,1)$ and $r\{0,1,2\} = \{3,1,0\}$ so $\{a_1,a_2\} = \{2,1\}$.

% Again too small. The problem is I don't think that it is in general true that some permutation of the list $r(i-1) - r(i)$ will be the list of lengths of columns of $\lambda_1$ followed by the list of lengths of columns of $\lambda_2$ which is what we are looking for. For one thing there's in general more than one way to write a partition as a sum of two partitions. Ok, concretely, a third example. Take $\lambda_1 = (a,b)$ and $\lambda_2 = (c,d)$ then $\lambda = (a + c, b + d)$ and 
% $$r\{0,1,\dots,a + c\} = \{N, N-2, \dots, N-2(b+d), N-2(b+d) - 1,\dots, 0\}$$
% so 
% $$\{a_1,a_2,\dots\} = \{2,2,\dots,2,1,1,\dots,1\}$$
% with $b+d$ 2s and $a+c - b - d$ 1s. Wait a minute, nevermind, of course this is true. We have two partitions $\lambda_1$ and $\lambda_2$ and one way to form the partition $\lambda = \lambda_1 + \lambda_2$ is to break $\lambda_i$ down into columns, order the columns by length, and recombine. Cool. I think it's fine. 
\acom{That's it for the note.}

@@

\begin{lemma} \label{le:Wmu}
    Let $ L \in \Grth^+$.  The following are equivalent:
    \begin{enumerate}
        \item $ L \in \cW_\mu$.
                \item $ L = \Sp_\cO(v_1, \dots, v_m)$ for some $ v_i $ of the form $ v_i = t^{\mu_i} e_i + \sum_{j=1}^m p_{ij} e_j $ where $ p_{ij} \in \CC[t] $ has degree less than $ \min(\mu_i, \mu_j)$. \acom{Do we want to sum over $j \ne i$ here? Maybe nvm because in $\TT_\mu$ the diagonal blocks can have $*$'s in the last row. Also $\cO$ should be $\CC[t]$.}
        \item  For all $ i $, 
        $$ t^{\mu_i} e_i \in \Sp_\CC(\{t^k e_j : 0 \le k < \min(\mu_i, \mu_j), 1 \le j \le m \}) + L. $$
    \end{enumerate}
    Moreover, for such $L $, $ \beta_\mu := \{ [t^k e_i] : 0 \le k < \mu_i, 1 \le i \le m\}$ forms a basis for $ L_0/L$.
\end{lemma}

@@

\begin{proof}
    Let $ L \in \cW_\mu$.  Then $ L = \Sp_\cO(v_1, \dots, v_m) $ for some $ v_i $ with $ v_i = t^{\mu_i} e_i + \sum_{j=1} q_{ij}t^{\mu_i} e_j $ and $ q_{ij} \in t^{-1} \Oinf$.  Since $ L \in \Grth^+ $, we see that $ v_i \in L_0$ which means that $ p_{ij} := q_{ij}t^{\mu_i} $ lies in $ \CC[t]$.  By construction, the polynomial $ p_{ij}$ has degree less than $ \mu_i$.

@@

\begin{proof}
    Let $ L $ lie in this image.  Then $ L = g t^{\mu_1} (t-s)^{\mu_2}$ fom some $ g \in N(\CC[t, t^{-1}, (t-s)^{-1}]) $.  Let $ h =(t-s)^{\mu_2} t^{-\mu_2}  $.  Note that $ h \in T_1(\Oinf)$. 
    Moreover,
    $$ L = h (h^{-1} g h) t^{\mu}\,. $$
    Note that 
    % $ h^{-1} g h \in N(\CC\xT[t^{-1}])$ 
    $h^{-1} g h \in N(\cK_\infty)$ and from \cite{kamnitzer2014yangians} 
    \jcom{Check this}, we know that $ (h^{-1} g h) t^{\mu} \in \cW_\mu$ and so the result follows.

    \acom{
        % The argument from my thesis does not go through since $\cW_\mu$ is defined mod $\CC[t]$. More precisely, we still have $N(\Kinf) = N_1(\CC[t]) N(\CC\xt[t^{-1}])$ and so $h^{-1}g h=g_1g_2$ for some $g_1 \in N_1(\CC[t])$ for some $g_2\in N\xt[t^{-1}]$. But now we would like to write $g_2 t^\mu = t^\mu g_3$ for some $g_3\in\CC[t]$. Oh, but I guess we can also 
        To check this write $N(\Kinf) = N_1(\Oinf)N(\CC[t])$. Does it hold? If $\mu$ is dominant and $g\in N(\CC[t])$ then $gt^\mu = t^\mu g'$ for some $g'\in N(\CC[t])$.} % What is a textbook reference for these factorization claims? are they obvious; they seem obvi
        \jcom{Yes, that is correct.  I think that I once had Alex write out a careful proof of this fact.  It holds for any unipotent group.  The proof is by induction.}
    \end{proof}

\section{Climax}
Given $ A \in \TT_\mu$, recall the definition of $ g(A)$ given in \Cref{eq:mvyofa}.
% section ??.  
As $ g(A) \in M_n(\CC[t]) \cap G_1(\Oinf)$, we will regard $ g(A)$ as giving an element of $ \Grth^+ \cap \cW_\mu$.

@@

 On the other hand, if $ (g(A), s) \in S^{\mu_1, \mu_2}_\AA$, then we can write 
 $$
 g t^\mu r= n t^{\mu_1} (t-s)^{\mu_2}
$$
for some $ r \in G(\CC[t]), n \in N[t, t^{-1}, (t-s)^{-1}] $ and $ g = g(A)t^{-\mu}$.  Let $ h = (t-s)^{\mu_2} t^{-\mu_2}$ which lies in $ T_1\xt[t^{-1}] $.
Note that $ h^{-1}n h \in N(\Kinf)$, 
% ((t^{-1}))
so we can factor it as $ n = n_1 n_2 $, where $ n_1 \in N_1(\Oinf), n_2 \in N(\CC[t])$.  So then after doing a bit of algebra, we reach
$$
t^\mu r (t^{-\mu} n_2 t^\mu) t^{-\mu} = g^{-1} h n_1.
$$
The right hand side $ g^{-1} h n_1 $ lies in $ G_1(\Oinf) $.  Now on the left hand side, we know that since $ \mu $ is dominant $ t^{-\mu} n_2 t^\mu \in N(\CC[t])$.  
Moreover since $ \mu $ is dominant, we know that 
$$t^\mu G(\cO) t^{-\mu} \cap G_1(\Oinf) = N_1(\Oinf)\,.$$
% $$t^\mu G(\cO) t^{-\mu} \cap G_1(\CC\xt[t^{-1}]) = N_1(\CC\xt[t^{-1}]\,.$$
Thus, we deduce that $ g^{-1} h n_1 \in N_1(\Oinf)$ 
% $ g^{-1} h n_1 \in N_1(\CC\xt[t^{-1}])$ 
and hence $ g(A) \in N_1(\Oinf) t^{\mu_1} (t-s)^{\mu_2} $.  Given that we know that $ A \in \TT_\mu $, this implies that $ (A,s) \in \UU^{\mu_1, \mu_2}_\AA$ as desired.
\end{proof}

@@

\section{Falling Action} % Resolution
\begin{comment}
\begin{theorem}
    Let $\lambda_i\ge\mu_i$ be dominant ($i=1,2$), $\mu = \mu_1 +\mu_2$, and $\lambda =\lambda_1+\lambda_2$. 
    % I have an irrational dislike of ending sentences with subscripts --- can we fix this?
    There is an isomorphism 
    \begin{equation}
        \overline{\OO}_{\lambda_1,\lambda_2}\cap\TT_{\mu_1,\mu_2} \to \overline\Gr_\AA^{\lambda_1,\lambda_2}\cap \cW_{\mu_1,\mu_2}
    \end{equation}
    got by taking a $\mu\times\mu$ block matrix $A$ in the $s$-fibre $\overline{\OO_{\lambda_1,\lambda_2}^s}\cap\TT_{\mu_1,\mu_2}^s$ on the left to the representative of the $s$-fibre on the right defined by  
    \begin{equation}
        \begin{split}
            g &= t^{\mu_1} (t-s)^{\mu_2} + a(t) \\
            a_{ij}(t) &= - \sum_{k=1}^{\mu_i} A^k_{ji} t^{k-1}
        \end{split}
    \end{equation}
    where $A^k_{ji}$ is the $k$th entry from the left of the last row of the $\mu_j\times\mu_i$ block of $A$. 
\end{theorem}

@@

\begin{proof}
    % Copy Roger's proof.
    We have
\[
\begin{split}
    S_{\mu_1, \mu_2} & = N\xT[t^{-1}]t^{\mu_1}(t-s)^{\mu_2} \\
     & \subset T_1\xt[t^{-1}] N\xT[t^{-1}] t^{\mu_1} (t-s)^{\mu_2} \\
     & = T_1\xt[t^{-1}] N_1\xt[t^{-1}] t^{\mu_1} (t-s)^{\mu_2} \qquad \text{\cite[Lemma 2.3]{kamnitzer2014yangians}}\\
     & = B_1\xt[t^{-1}] t^{\mu_1} (t-s)^{\mu_2} \\
     & = B_1\xt[t^{-1}] t^{\mu_1 + \mu_2} \\
     & \subset G_1\xt[t^{-1}] t^{\mu_1 + \mu_2} \\
     & = W_{\mu_1 + \mu_2}
\end{split}
\]
where $B_1\xt[t^{-1}] t^{\mu_1} (t-s)^{\mu_2} = B_1\xt[t^{-1}] t^{\mu_1 + \mu_2}$ since 
\[
\frac{t}{t-s} = 
1 + \frac{s}{t} + \frac{s^2}{t^2} + \cdots 
\in B_1\xt[t^{-1}].
\]
\end{proof}
\end{comment}

@@

\acom{Plus fusion product of fake MV cycles for a fourth!}
